First and foremost, I would like to thank my advisor Michael R. Blanton. 
He very patiently guided me when I started graduate school and later gave me 
the freedom to explore on my own while always being available for guidance and 
wisdom when I needed it. I am extremely thankful for his amazing patience, 
encouragement, and thoughtful mentoring. 

I am deeply grateful to Roman Scoccimarro for his patient mentoring, his 
deep scientific intuitions, and his insightful yet pedagogical explanations whenever
I stepped into his office.
I am also very thankful to Jeremy L. Tinker for his warm mentoring, constant 
encouragement and support, and always having his door open for scientific discussions.
I would also like to thank David Hogg for his guidance, support, and unending energetic 
enthusiasm for science (even fiber collisions).

This dissertation and my graduate school career would not have been possible without 
the help of 
Dan Foreman-Mackey, 
Boris Leistedt, 
Maryam Modjaz, 
John Moustakas, 
Khee-Gan Lee, 
Fransisco Prada, 
Sergio Rodr\'{i}guez-Torres, 
Shenglong Wang, 
Andrew Wetzel, 
Renbin Yan, 
Guangtun Zhu, 
and many others. 

I would like to thank my classmates at NYU: 
Ruben Gepner, 
Mark Hannel, 
Oliver Janssen, 
Doycho Karagyozov, 
Alex Malz, 
Nityasri Mandyam, 
Christine Middleton, 
Geoffrey Ryan, 
Cato Sanford, 
Rob Speare, 
Mohammadjavad Vakili, 
Kilian Walsh, 
and many others. 
In addition to the intellectually stimulating environment and craic they provided, 
their friendships made my graduate school experience truly enjoyable. 
Outside of the department, I would also like to thank Adam, Eugene, 
Greg, Jasmine, Shyr, and Vinny for all the good times in NYC. 

Finally, I want to thank Lidia Cano, to whom this thesis is dedicated, for the 
unending love and support she has given me over the years. She has taught me 
so much about life. Without her by my side, I would not be where I am today. 

%Insert acknowledgement here.
%First, a huge thanks is in order for my advisor, David Hogg, for these years
%of support, encouragement, and friendship.
%I couldn't have imagined a better advisor for me and I'm looking forward to
%many years of collaboration.
%Hogg's enthusiasm is infectious and our lively discussions over lunch, coffee,
%or beer have convinced me to attempt a career in academia and made me a better
%scientist and person.
%
%I would also like to thank my other dissertation readers, Jonathan Goodman and
%Micheal Blanton, for taking the time to read my thesis and provide useful
%suggestions and clarifications that improved the presentation of this work.
%
%One of my favorite parts of studying astronomy is the community and the
%opportunities to meet and get to know amazing people from around the world.
%Over the course of my Ph.D.\ research, I have had the opportunity to
%collaborate with more people than I can possibly list here.
%I am especially grateful for the summers that I spent in Germany with Bernhard
%Sch\"olkopf and Hans-Walter Rix; the garden chats in T\"ubingen and Heidelberg
%were some of the highlights of my scientific career thus far.
%I have also enjoyed and benefited from conversations and collaborations with
%Brendon Brewer,
%Tom Barclay,
%Charlie Conroy,
%Bekki Dawson,
%Eric Ford,
%Morgan Fouesneau,
%Jonathan Goodman,
%Dustin Lang,
%Phil Marshall,
%Ben Montet,
%Tim Morton,
%Mike O'Neil,
%Adrian Price-Whelan,
%Elisa Quintana,
%Jonathan Sick,
%Dan Weisz,
%and many others.
%
%My time spent living in NYC wouldn't have been the same without my eclectic
%(and perfectly eccentric) group of housemates and friends.
%In particular, I'd like to thank Mira, Stefan, Nate, Claire, Katherine, Jacob,
%Silas, and Stumm for all the good times on Dean Street.
%I would also like to thank Ruth for being there for me when I needed her and
%sharing in life and in science, even from the opposite side of the ocean.
%
%Finally, I would like to thank my family, Annie, Clarke, and Elaine for their
%continued love, encouragement, and support every step of the way.
%I would never have made it here without them!
